Parallel Hierarchical Clustering using \\ Rank-Two Nonnegative Matrix Factorization \thanks{Identify applicable funding agency here. If none, delete this.}

### 2020-07-16 latex/tex/experiments.tex
little edits
briging down to 10 pages

\begin{figure}
\begin{center}
\includegraphics[height=2in, width=\columnwidth]{plots/dc_hierarchical_speedup.pdf}
\caption{Strong Scaling Speedup for Hierarchical Clustering on \hyper{}}
\label{fig:dcspeedup}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[height=2in, width=\columnwidth]{plots/synthetic_rank2_speedup.pdf}
\caption{Strong Scaling Speedup for Rank-2 NMF on Synthetic Data}
\label{fig:synrank2speedup}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[height=2in, width=\columnwidth]{plots/synthetic_rank2_strongscaling.pdf}
\caption{Relative Time Breakdown for Rank-2 NMF on Synthetic Data}
\label{fig:synrank2strongscaling}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[height=2in, width=\columnwidth]{plots/realworld_rank2_speedup.pdf}
\caption{Strong Scaling Speedup for Rank-2 NMF on \image{} Data}
\label{fig:rwrank2speedup}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[height=2in, width=\columnwidth]{plots/realworld_rank2_strongscaling.pdf}
\caption{Relative Time Breakdown for Rank-2 NMF on \image{} Data}
\label{fig:rwrank2strongscaling}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[height=2in, width=\columnwidth]{plots/synthetic_hierarchical_speedup.pdf}
\caption{Strong Scaling Speedup for Hierarchical Clustering on Synthetic Data}
\label{fig:synhierspeedup}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[height=2in, width=\columnwidth]{plots/synthetic_hier_strongscaling.pdf}
\caption{Relative Time Breakdown for Hierarchical Clustering on Synthetic Data}
\label{fig:synhierstrongscaling}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[height=2in, width=\columnwidth]{plots/realworld_hierarchical_speedup.pdf}
\caption{Strong Scaling Speedup for Hierarchical Clustering on \image{} Data}
\label{fig:rwhierspeedup}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[height=2in, width=\columnwidth]{plots/realworld_hier_strongscaling.pdf}
\caption{Relative Time Breakdown for Hierarchical Clustering on \image{} Data}
\label{fig:rwhierstrongscaling}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[height=2in, width=\columnwidth]{plots/synthetic_sequential_level_breakdown.pdf}
\caption{Levels Breakdown Timings for 1 Compute Node on Synthetic Data}
\label{fig:seqlevelbreakdown}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[height=2in, width=\columnwidth]{plots/synthetic_parallel_level_breakdown.pdf}
\caption{Levels Breakdown Timings for 40 Compute Nodes on Synthetic Data}
\label{fig:parallellevelbreakdown}
\end{center}
\end{figure}

%\begin{figure}
%\begin{center}
%\includegraphics[height=2in, width=\columnwidth]{plots/realworld_parallel_level_breakdown.pdf}
%\caption{Levels Breakdown Timings for 80 Compute Nodes on \image{} Data}
%\label{fig:rwparallellevelbreakdown}
%\end{center}
%\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics[height=1.5in, width=\columnwidth]{plots/dc_hierarchical_speedup.pdf}
\caption{Strong Scaling Speedup for Hierarchical Clustering on \hyper{}}
\label{fig:dcspeedup}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{subfigure}{1.5in}
\begin{center}
\includegraphics[height=1.4in, width=1.4in]{plots/synthetic_rank2_speedup.pdf}
\caption{Synthetic Data}
\label{fig:synrank2speedup}
\end{center}
\end{subfigure}
\begin{subfigure}{1.5in}
\begin{center}
\includegraphics[height=1.4in, width=1.4in]{plots/realworld_rank2_speedup.pdf}
\caption{\image{} Data}
\label{fig:rwrank2speedup}
\end{center}
\end{subfigure}
\caption{Strong Scaling Speedup for Rank-2 NMF }
\label{fig:rank2speedup}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[height=1.5in, width=\columnwidth]{plots/synthetic_rank2_strongscaling.pdf}
\caption{Relative Time Breakdown for Rank-2 NMF on Synthetic Data}
\label{fig:synrank2strongscaling}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[height=1.5in, width=\columnwidth]{plots/realworld_rank2_strongscaling.pdf}
\caption{Relative Time Breakdown for Rank-2 NMF on \image{} Data}
\label{fig:rwrank2strongscaling}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{subfigure}{1.5in}
\begin{center}
\includegraphics[height=1.4in, width=1.4in]{plots/synthetic_hierarchical_speedup.pdf}
\caption{Synthetic Data}
\label{fig:synhierspeedup}
\end{center}
\end{subfigure}
\begin{subfigure}{1.5in}
\begin{center}
\includegraphics[height=1.4in, width=1.4in]{plots/realworld_hierarchical_speedup.pdf}
\caption{\image{} Data}
\label{fig:rwhierspeedup}
\end{center}
\end{subfigure}
\caption{Strong Scaling Speedup for Hierarchical Clustering}
\label{fig:rank2speedup}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[height=1.5in, width=\columnwidth]{plots/synthetic_hier_strongscaling.pdf}
\caption{Relative Time Breakdown for Hierarchical Clustering on Synthetic Data}
\label{fig:synhierstrongscaling}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[height=1.5in, width=\columnwidth]{plots/realworld_hier_strongscaling.pdf}
\caption{Relative Time Breakdown for Hierarchical Clustering on \image{} Data}
\label{fig:rwhierstrongscaling}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[height=1.5in, width=\columnwidth]{plots/synthetic_sequential_level_breakdown.pdf}
\caption{Levels Breakdown Timings for 1 Compute Node on Synthetic Data}
\label{fig:seqlevelbreakdown}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[height=1.5in, width=\columnwidth]{plots/synthetic_parallel_level_breakdown.pdf}
\caption{Levels Breakdown Timings for 40 Compute Nodes on Synthetic Data}
\label{fig:parallellevelbreakdown}
\end{center}
\end{figure}

%\begin{figure}
%\begin{center}
%\includegraphics[height=1.5in, width=\columnwidth]{plots/realworld_parallel_level_breakdown.pdf}
%\caption{Levels Breakdown Timings for 80 Compute Nodes on \image{} Data}
%\label{fig:rwparallellevelbreakdown}
%\end{center}
%\end{figure}
